\todo{Something} presents OpenAdcess

### 2017-02-09 digital-library.tex

\subsection{Fake Download Buttons}
Fake download buttons are a staple of modern download websites.
By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression.

@@

Lastly, we are revolutionising the fake download practice by dynamically
randomizing the position of the actual download button.
Like serving ad content natively, this will make ad blockers functionally
useless as there will be no way to differentiate between ad content and ACM
content.
Moreover, this randomization makes it much harder for the user to learn the
positioning of the ads and therefore we hope to drive more clicks to our ad
partners and generate more revenue for the ACM.

>>>>

\subsection{Fake Download Buttons}

Fake download buttons are a staple of modern download websites. They really class up the web. Reifying, elegizing, and idealizing nature, these abstract forms with rococo garnishes direct the downloader's attention away from the url to the ad-serving service to which the button points. A deceptive d\'{e}tournement, the premonitory placement of these blissed-out buttons challenges browsers to consider whether they really want to download the paper -- they could, after all, not pursue their line of inquiry and instead watch it evolve vicariously -- which cuts down on the ACM's hosting costs.

By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression. Some regulators have questioned this practice. But we believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of the National Economic Council, stressed in an interview with *The Wall Street Journal* compared a website without fake-download buttons to the menu at P.J. Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good. But you still shouldn?t eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically. It should be impossible for consumers to access independent, third-party statistics about menu items. ``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them. We don't want the government treating them like dotards," the Gary Cohns said in unison.}.

@@

Lastly, we are revolutionizing the fake download practice by dynamically
randomizing the position of the actual download button.
Like serving ad content natively, this will make ad blockers functionally
useless as there will be no way to differentiate between ad content and ACM
content, providing users with instruction on the contingency of fate.
Moreover, this randomization makes it much harder for the user to learn the
positioning of the ads and therefore we hope to drive more clicks to our ad
partners and generate more revenue for the ACM.

### 2017-02-09 future-work.tex

\section{Future Work}
We lifted this paper from a future edition of SIGTBD \todo{citation to future
paper edition}.
We believe that researchers today make too little use of time machines.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/mill.png}
  \caption{ACM work dungeon mill powered by 5th year grad student}
  \label{fig:mill}
\end{figure}

@@

\subsection{ACM Seizes Means of Production}
\todo{By putting crushed crystals in CEO's coffee, the ACM will influence CEOs
  to liquidate their companies and give them to the ACM.
  The mills were originally for crushing crystals but after the revolution they
were re purposed to generate electricity}

>>>>

\section{Future Work}
This future work appears in SIGTBD \todo{citation to future
paper edition}.

@@

\subsection{Introduction}
\paragraph{Introduction} An introduction is an explanatory section of a document that introduces the topic discussed in the document and presents a thesis statement.
\paragraph{Antithesis} Think about it, man. There is not introduction. We just see bad writing, cast as we are into this broken world.
\paragraph{Sublation} The introduction, some may argue

We think introductions leave those catching up with a field disoriented. More theater than truth, these sections do little to erase the veil of nonseeing from the student's mandatory raised unibrow, but -- please take a moment to recognize the taste of ACM Cola or the cool, refreshing ACM technology deity which (for all you just tuning in who forgot your mandatory religious training) we call Jerry -- the introduction

the boundless territory of

As you may recall from \todo{sublation}, the engineers have ended the industrial dictatorship of the captains of finance as a matter of convenience

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/mill.png}
  \caption{ACM work dungeon mill powered by 5th year grad student. Notice how our graduate students show great vigor and -- auscultate away! -- don't sound consumptive.}
  \label{fig:mill}
\end{figure}

@@

\subsection{ACM Seizes Means of Production}
\todo{By putting crushed crystals in CEO's coffee, the ACM will influence CEOs
  to liquidate their companies and give them to the ACM.
  The mills were originally for crushing crystals but after the revolution they
were re purposed to generate electricity
ESPN executives are Mormon though and impervious to crystal healing and coffee. So we had to compromise: the entire National Park System became an ESPN Zone.
}
